---
output: github_document
---

# Introduction
In this package, you can get various Marvel data from Marvel API, including characters, events, comics and series in Marvel.
There are five functions in the package: `MarvelCharacters`, `InfoMarvelCharacters`, `InfoMarvelEvents`, `InfoMarvelComics`, `InfoMarvelSeries`. 

# First...
First of all, you should get an API key <https://developer.marvel.com/>. Following the instruction, you will get a public key and a private key. 


# Function: MarvelCharacters
In this function, you will send several request to Marvel API, and get a dataset including all characters and their brief description in Marvel cosmic (total 1491). If you have no idea about Marvel and Marvel heroes, this function is your best choice. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(httr)
library(digest)
library(jsonlite)
library(tidyverse)
library(stringr)
```


```{r echo=TRUE, message=FALSE, warning=FALSE}
library(MarvelData)
MarvelData <-MarvelCharacters(Sys.getenv("MARVEL_PUBLIC_KEY"),Sys.getenv("MARVEL_PRIVATE_KEY"))
head(MarvelData,n=20)
```

You can choose a character who interests you and get more information in following functions.


# Functions: InfoMarvelCharacters
In this function, you will send a request to Marvel API, and get a dataset including one character's name, description and events, comics and series that contains the character.
There are four arguments in this function: Character's name, your public key, your private key, and showing more detail info of events, comics and series. In the forth argument, you have four choices:
1.Keep it blank.
In this condition, you will get a dataset only including character's name and description.
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(MarvelData)
InfoMarvelCharacters("Thor",Sys.getenv("MARVEL_PUBLIC_KEY"),Sys.getenv("MARVEL_PRIVATE_KEY"))
```

2.Events
In this case, you will get a dataset including some events that contains your character.
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(MarvelData)
InfoMarvelCharacters("Thor",Sys.getenv("MARVEL_PUBLIC_KEY"),Sys.getenv("MARVEL_PRIVATE_KEY"),"events")
```
The output of this example is a dataset including some events that contains Thor.

3.Comics
In this case, you will get a dataset including some comics that contains your character.
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(MarvelData)
InfoMarvelCharacters("Thor",Sys.getenv("MARVEL_PUBLIC_KEY"),Sys.getenv("MARVEL_PRIVATE_KEY"),"comics")
```
The output of this example is a dataset including some comics that contains Thor.

4.Series
In this case, you will get a dataset including some series that contains your character.
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(MarvelData)
InfoMarvelCharacters("Thor",Sys.getenv("MARVEL_PUBLIC_KEY"),Sys.getenv("MARVEL_PRIVATE_KEY"),"series")
```
The output of this example is a dataset including some series that contains Thor.


# Function: InfoMarvelEvents
Same as function `InfoMarvelCharacters`, this function will show you a dataset related with a event. Besides event's title, description, start year and end year, you can request more information of characters included in the event and comics and series that contains the event.
There are four arguments in this function: Event's title, your public key, your private key, and showing more detail info of characters, comics and series. In the forth argument, you have four choices: "characters", "comics", "series" or keep it blank(default).

For examples:
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(MarvelData)
InfoMarvelEvents("Civil%20War",Sys.getenv("MARVEL_PUBLIC_KEY"),Sys.getenv("MARVEL_PRIVATE_KEY"))
```
The output is a dataset including Civil War's description, start year and end year(in real time).
__Attention__: when you input event's title, if there is a blank in the title, you should use %20 to replace the blank.(Same as characters, series and comics' title)
For example, the event's title is "Civil War". The input of function should be "Civil%20War".

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(MarvelData)
InfoMarvelEvents("Civil%20War",Sys.getenv("MARVEL_PUBLIC_KEY"),Sys.getenv("MARVEL_PRIVATE_KEY"),"series")
```
In this example, you will get a dataset about series that contains Civil War.


# Function: InfoMarvelComics
In this function, you will get a lot of data of one comics topic. The output of this function is a dataset contains comics'title, description, issuenumber and format.
You should input one comics' title(do not need input the number of this comics).
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(MarvelData)
ComicsData <- InfoMarvelComics("Amazing%20Spider-Man",Sys.getenv("MARVEL_PUBLIC_KEY"),Sys.getenv("MARVEL_PRIVATE_KEY"))
head(ComicsData,n=20)
```


# Function: InfoMarvelSeries
In this function, you will get a dataset including one series title, description, start year, end year, rating and type.
```{r echo=TRUE, message=FALSE, warning=FALSE}
InfoMarvelSeries("Black%20Panther",Sys.getenv("MARVEL_PUBLIC_KEY"),Sys.getenv("MARVEL_PRIVATE_KEY"))
```

